\bf Title

### 2023-10-03 article/paper_padic_spec.tex
added ref in bib

%\usepackage{amsthm}
\newenvironment{proof}{\hbox{}\vspace{-0.5cm} {\bf Proof:}}{\hfill $\Box$ \\}

@@

\newcommand{\simone}[1]{{\color{blue} #1}} % simone's comments
\newcommand{\corentin}[1]{{\color{red} #1}} % simone's comments
\newcommand{\tristan}[1]{{\color{olive} #1}} % simone's comments

@@

\author{$^{1,2}$,  $^3$}

\footnotetext[1]{CNRS; LAAS; Universit\'e de Toulouse, 7 avenue du colonel Roche, F-31400 Toulouse, France. }

@@

\section{Introduction}

\end{document}

>>>>

\newenvironment{proof}{\hbox{}\vspace{-0.5cm} {\bf Proof:}}{\hfill $\Box$ \\}

@@

\newcommand{\simone}[1]{{\color{blue} #1}} % simone's comments
\newcommand{\corentin}[1]{{\color{red} #1}} % corentin's comments
\newcommand{\tristan}[1]{{\color{olive} #1}} % tristan's comments

\usepackage{biblatex}
\addbibresource{../rapport/bibstage.bib}

@@

\author{Corentin Cornou$^{1}$, Simone Naldi$^2$ and Tristan Vaccon$^2$}

\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay.}
\footnotetext[2]{Université de Limoges, CNRS, XLIM, Limoges, France.}

@@

\section{Introduction}
\subsection{Motivations and main results}
\subsection{Real spectrahedra}

\section{Notation}

\section{Polyhedra and linear programming}

\subsection{Polyhedra}
\subsection{Linear programmming}

\section{Spectrahedra}

\subsection{Definition}
\subsection{Annuli (couronnes)}
\subsection{Polyhedrality}
Cf. \cite{bhardwaj2015deciding}

\printbibliography
\end{document}
